Constructing a universe for the setoid model

### 2020-07-06 paper.tex
typos

The universe constructions presented in this paper are, to our knowledge, the
first examples of two kinds of data type reductions in an intensional
metatheory: the first involving an inductive-recursive type which including
strict propositions, and the second involving an infinitary inductive-inductive
type.

@@

\section{$\mlttp$}\label{metatheory}

@@

\section{Setoid model}\label{setoid-model}

>>>>

The universe constructions presented in this paper are, to our knowledge, the
first examples of two kinds of data type reductions in an intensional
metatheory: the first involving an inductive-recursive type which includes
strict propositions, and the second involving an infinitary inductive-inductive
type.

@@

\section{$\mlttp$}\label{sec:metatheory}

@@

\section{Setoid model}\label{sec:setoid-model}
